---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DoubleHelix

<!-- badges: start -->
<!-- badges: end -->
The goal of `DoubleHelix` is to provide a quick and easy way to create engaging visual resources, including figures, GIFs, and formulas, based on the theory of quantitative genetics.

This package aims to make these resources more accessible to instructors and students, supporting teaching and learning in genetics and quantitative genetics through intuitive and customizable visualizations.


## Installation

You can install the development version of `DoubleHelix` from [GitHub](https://github.com/filipe-manoel/DoubleHelix) with:

``` r
# install.packages("pak")
pak::pak("filipe-manoel/DoubleHelix")

```

## Example 1

This is how you can plot and export some common covariance matrices structures.

```{r example1}
library(DoubleHelix)

#Compound Simetry matrix
plot_cs(n = 5, rho = 0.5, save_path = NULL, width = 5, height = 5, dpi = 300)

#Unstructured matrix
plot_us(n = 5, save_path = NULL, width = 5, height = 5, dpi = 300)

#First order factor analytic matrix
plot_fa(n = 5, k = 1, save_path = NULL, width = 5, height = 5, dpi = 300)

```

## Example 2

By using `plot_cov_operations`, you can plot figures representing operations with covariance matrices.

```{r, example2, results='hide' }
library(DoubleHelix)

cov1 = plot_diagonal(n=3)
cov2 = plot_ar1(n=5, rho=0.7)
```

```{r example3 }
plot_cov_operations(cov1 = cov1, cov2 = cov2, op="kronecker")
```

## Development Status

This package is in active development and currently in an experimental stage.

Contributions are welcome!
Feel free to fork the repository, submit pull requests, or open issues via [GitHub](https://github.com/filipe-manoel/DoubleHelix).


## License

This package is released under the [MIT License](https://opensource.org/licenses/MIT).


