---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DoubleHelix

<!-- badges: start -->
<!-- badges: end -->

The goal of `DoubleHelix` is to allow the quick and easy creation of visual resources (figures, gifs and formulas) based on the theory of quantitative genetics.

The idea is to have this resources more accessible to instructors in teaching genetics and quantitative genetics.

## Installation

You can install the development version of `DoubleHelix` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("filipe-manoel/DoubleHelix")

```

## Examples


This is how you can plot and export to your local directory some common covariance matrices structures.

```{r example}
library(DoubleHelix)

#Compound Simetry matrix
DoubleHelix::plot_cs(n = 5, rho = 0.5, save_path = NULL, width = 5, height = 5, dpi = 300)

#Unstructured matrix
DoubleHelix::plot_us(n = 5, save_path = NULL, width = 5, height = 5, dpi = 300)

#First order factor analytic matrix
DoubleHelix::plot_fa(n = 5, k = 1, save_path = NULL, width = 5, height = 5, dpi = 300)

```





